---
title: ''
output: html_document
---

## Data Cleaning For World Wealth 2019 Dataset

I downloaded the dataset from Makeover Monday from [data.world](https://data.world/makeovermonday/2020w7-world-wealth).

I used the cleaned dataset for visualisation which I published to [Tableau Public](https://public.tableau.com/profile/steffen.zou.weilun#!/vizhome/TotalWealthByRegionCountryIn2019/TotalWealthByRegionCountryIn2019).

```{r message=FALSE}
library(readxl)
library(writexl)
library(dplyr)

world_wealth <- read_excel('WorldWealth.xlsx', sheet='WorldWealth')
saved_column_names <- names(world_wealth)
names(world_wealth) <- tolower(gsub('[ ()$]', '', names(world_wealth)))
```


## Remove Row With Missing Wealth

```{r}
filter(world_wealth, is.na(wealthb))
```

```{r}
world_wealth <- filter(world_wealth, !is.na(wealthb))
sum(is.na(select(world_wealth, wealthb)))
```


## Remove Dollar Sign And Comma From Wealth Column And Convert To Integer Type

```{r}
world_wealth <- mutate(world_wealth, wealthb=as.numeric(gsub('[$,]', '', wealthb)))
```

## Update Region 'China' and 'India' To 'Asia-Pacific'

```{r}
select(world_wealth, region) %>% unique()
```

```{r}
filter(world_wealth, region %in% c('China', 'India'))
```
I verified that China and India are in the list of countries of the Asia-Pacific region. URL is https://apcss.org/about/ap-countries/.

```{r}
world_wealth <- mutate(world_wealth
                       , region=ifelse(region %in% c('China', 'India')
                                       , 'Asia-Pacific', region))

filter(world_wealth, country %in% c('China', 'India'))
```


## Save Cleaned Data Set As A New File

```{r}
names(world_wealth) <- saved_column_names
write_xlsx(list(WorldWealth = world_wealth), 'WorldWealth_cleaned.xlsx'
           , format_headers = FALSE)
```

